### 2024-10-02 paper-en.tex
Fix algorihtm 2

\graphicspath{{paper_images/}}
\newtheorem{theorem}{Theorem}
\newtheorem{notice}{Notice}

@@

\begin{equation}
    \centering
    \left\{
        \begin{array}{ll}
            x_1 - x_2 &\neq 0             ; \\
            x_3 - x_4 &\neq 0             ; \\
            2 x_1 - 2 x_2 &\neq 0         ; \\
            2 x_3 - 2 x_4 &\neq 0         ; \\
            x_1 - x_2 - x_3 + x_4 &\neq 0 ; \\
            x_1 - x_2 + x_3 - x_4 &\neq 0 . \\
        \end{array}
        \label{eqs:cycle_search_neqs}
    \right.
\end{equation}

@@

\begin{enumerate}
    \item Let $e$ be the number of variables in a system of inequalities.
    \item If the system contains inequality $0 \neq 0$ then it has no solution, the algorithm halts.
    \item Let us pick all inequalities of the form $a x_e + b \neq 0$. Let $I$ be the set of all such inequalities.
    \item Let $v$ be a number such that $v \neq -b/a \forall a x_e + b \in I$, if $I = \varnothing$, then let $v = 0$. Such a number can be found because there is a finite amount of inequalities.
    \item Substitute variable $x_e$ with value $v$ in all inequalities and add identity $x_e = v$ to solution. By $v$ selection conditions, none of inequalities will turn into $0 \neq 0$ by such a substitution. 
    \item If $e = 1$ the algorithm halts, otherwise let $e = e - 1$ and return to step 3.
\end{enumerate}

\textbf{Пример.}

Let $x_1$ be $0$, substitute it in a system of inequalities.

@@

Variable $x_2$ can not be equal to $0$, because it violates inequality $- x_2 \neq 0$. Let $x_2$ be $1$, substitute it in a system of inequalities.

@@

Let $x_3$ be $0$, substitute it in a system of inequalities.

@@

Variable $x_4$ can not be equal to $0, 1, -1$, because it violates inequalities. Let $x_4$ be $2$, substitute it in a system of inequalities:

@@

Given inequalities do not allow $r$ to be $1, 2, 3, 4$, thus the least possible value of $r$ is $5$. 5-expansion of metagraph with weights, obtained as a solution to system (1), is shown in figure \ref{neq_system_res}. Girth of this graph is equal to $6$, and one of the cyc;es with length $6$ is marked in bold.

@@

        \thicklines
        \bezier{300}(50,165)(77,100)(105,35)
        \bezier{300}(120,165)(112,100)(105,35)
        \bezier{300}(120,165)(147,100)(175,35)
        \bezier{300}(190,165)(182,100)(175,35)
        \bezier{300}(190,165)(197,100)(205,35)
        \bezier{300}(50,165)(127,100)(205,35)
    \end{picture}
    \caption{ Expansion of a metagraph with weights obtained as a solution of a system of inequalities. }
    \label{neq_system_res}
\end{figure}

>>>>

\graphicspath{{paper_images/}}
\newtheorem{theorem}{Theorem}
\newtheorem{notice}{Remark}

@@

\begin{equation}
    \centering
    \left\{
        \begin{array}{ll}
            x_1 - x_2 &\neq 0             (\mod{r}) ; \\
            x_3 - x_4 &\neq 0             (\mod{r}) ; \\
            2 x_1 - 2 x_2 &\neq 0         (\mod{r}) ; \\
            2 x_3 - 2 x_4 &\neq 0         (\mod{r}) ; \\
            x_1 - x_2 - x_3 + x_4 &\neq 0 (\mod{r}) ; \\
            x_1 - x_2 + x_3 - x_4 &\neq 0 (\mod{r}) . \\
        \end{array}
        \label{eqs:cycle_search_neqs}
    \right.
\end{equation}

@@

At first consider system \eqref{eqs:example} without parameter $r$. Find a solution using the following steps

\begin{enumerate}
    \item Let $e$ be the number of variables in a system of inequalities.
    \item If the system contains inequality $0 \neq 0$ then it has no solution, the algorithm halts.
    \item Select all inequalities of the form $a x_e + b \neq 0$. Denote the set of all such inequalities as $I$.
    \item Let $v$ be a number such that $v \neq -b/a $ for each inequality $"a x_e + b \neq 0" \in I$. In case $I = \varnothing$ assign $v = 0$. Such a number can be found since $I$ is finite.
    \item Substitute value $v$ instead of variable $x_e$ in all inequalities and add equality $x_e = v$ to the solution. By $v$ selection conditions, none of inequalities will turn into $0 \neq 0$ by such a substitution. 
    \item If $e > 1$ assign $e = e - 1$ and return to step 3, otherwise the solution is found, proceed to calculation of parameter $r$.
\end{enumerate}

Substitute found solution to system \eqref{eqs:example}, denote the obtained system as $I_s$. All inequalities have form $a \neq 0 (\mod{r})$ where $r$ is an unknown parameter. Form of inequalities allow us to find it as $r = \max\limits_{"a \neq 0 (\mod{r})" \in I_s}\{ |a| \} + 1$.

Consider system of inequalities \eqref{eqs:cycle_search_neqs}.

Assign $x_1 = 0$. Recalculate considered system with assigned value. We get

@@

Variable $x_2$ can not be equal to $0$ since it would violate inequality $- x_2 \neq 0$. Assign $x_2 = 1$. We obtain

@@

Assigning $x_3 = 0$ similarly, we get

@@

Variable $x_4$ can not be equal to $0, 1$ and $-1$ since they violate the last inequalities. Assign $x_4 = 2$. We finally obtain

@@

% TODO: пронумеровать примеры и вставить нормальную ссылку

This system does not allow $r$ to be $1, 2, 3$ and $4$, thus the least possible value of $r$ is $5$. 5-expansion of metagraph $G$ considered in example $<ref>$ with assigned weights, is shown in figure \ref{neq_system_res}. Girth of this graph is equal to $6$, and one of the cycles with length $6$ is marked in bold.

@@

        \thicklines
        \bezier{300}(50,165)(77,100)(105,35)
        \bezier{300}(120,165)(112,100)(105,35)
        \bezier{300}(120,165)(147,100)(175,35)
        \bezier{300}(190,165)(182,100)(175,35)
        \bezier{300}(190,165)(197,100)(205,35)
        \bezier{300}(50,165)(127,100)(205,35)
    \end{picture}
    \caption{ Expansion of a metagraph with weights obtained as a solution of the system \eqref{eqs:cycle_search_neqs}. }
    \label{neq_system_res}
\end{figure}
